Implementation of Parallel Algorithms for ARIMA in Distributed Database Systems

### 2013-10-05 draft.tex
Continue

It is very easy to see that Eqs.
(\ref{eq:error-terms},~\ref{eq:J1},~\ref{eq:J2},~\ref{eq:J3}) are
difficult to parallelize. Each step computation uses the result from
the previous step. Therefore, we have to scan through the data
sequentially to compute the quatities in these equations. If the data
set is very large then it

@@

>>>>

It is very easy to see that Eqs.
(\ref{eq:error-terms},~\ref{eq:J1},~\ref{eq:J2},~\ref{eq:J3}) are
difficult to parallelize. Each step computation uses the result from
the previous step. Therefore, we have to scan through the data
sequentially to compute the quatities in these equations, and we have
to do this in every iteration. If the data set is very large then it
is time-consuming to use this algorithm.

@@

% We may not be able to use Alpine's name here

Some comments about Alpine: Alpine is consistently two to threetimes
faster than MADlib on GPDB.\@ However, Alpine's result is usually very
bad if not wrong.
